Evaluation of performances

### 2019-12-09 analysis/eval-performance.Rmd
Standard Error -> SE

```{r eval-performance-1, warning=FALSE}
table1 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "Standard Error" = se,
  ) %>%
  ungroup() %>% 
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`, -rsq, -expvar) %>% 
  arrange(RMSE)

@@

```{r eval-performance-2, warning=FALSE}
table2 <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group) %>%
  slice(which.min(rmse.test.rmse)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse.test.rmse) %>%
  dplyr::rename(
    "Learner Group" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse.test.rmse
  ) %>%
  select(-6) %>%
  select(-`Learner ID`)

@@

table2 %>%
  flextable()
```

>>>>

```{r eval-performance-1, warning=FALSE}
table1 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  ungroup() %>% 
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`, -rsq, -expvar) %>% 
  arrange(RMSE)

@@

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>% 
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  select(-rsq, -expvar, -iter) %>%
  select(-`Learner ID`)

@@

table2 %>%
  flextable() %>% 
  autofit()
```
